---
title: "Deliverable Team II"
output: pdf_document
date: "2025-02-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results = "hide")
```

# 1.1 Research Motivation 

## Research Question:

How are customer reviews affected by the opening hours of restaurants in Illinois?

### Sub-Questions:

1.  How are star ratings affected by the opening hours of restaurants in Illinois?
2.  How is the sentiment of customer reviews affected by the opening hours of restaurants in Illinois?

### Background

This quantitative research will take a look at the effect of opening hours of restaurants on customer reviews. Restaurants from all over the world can benefit from this study through better understanding of factors that influence customer reviews. In many cases new customers rely on the reviews of other customers for selecting restaurants, where highly praising reviews increase conversion rates and negative reviews deter purchases. The star rating of reviews will be logistic regressed on the opening hours of restaurants to find the answer to sub question 1. Using sentiment analysis on the written customer reviews will provide a idea of what is being discussed and the effect of opening hours on this sentiment can be analysed with an ordinal logistic regression model.

## Research Method:

For sub question 1, our dependent variable is star rating. This will be a categorical variable as we will them group into high star rating (4-5 stars) and low star rating (1-3 stars). The independent variable is opening hours, which is also categorical. The total amount of hours a restaurant is opened, will be counted. Two groups will be separated: high / low amount of opened hours. Because both the dependent variable star rating and the independent variable opening hours are categorical a binary logistic model will return the relationship and give predictability scores. For sub question 2, our dependent variable is the sentiment of customer reviews. This will be a categorical variable with 3 groups which have a natural order (negative \< neutral \< positive). The independent variable is opening hours, similar to question 1. An ordinal logistic regression model will be used for sub question 2. Customer reviews are categorized into 3 ordinal levels and opening hours into two levels. The result of this model will give the probabilities of sentiment levels based on the opening hours of a restaurant.

# 2.1 Data Exploration 

Firstly, several packages are loaded into our Rstudio. 

```{r}
library(tidyverse)
library(dplyr)
library(here)
library(stringr)
```

Four our research, we only need the business dataset and review dataset of Yelp, which we downloaded from https://business.yelp.com/data/resources/open-dataset/  

```{r}
Data_Bus <- read_csv(here("data", "yelp_academic_dataset_business.csv"))
Data_Review <- read_csv(here("data","yelp_academic_dataset_review.csv"))
```

As both datasets contained a business_id variable, we merged them together by business_id.

```{r}
Data_Merged <- merge(Data_Bus, Data_Review, by = "business_id", all = TRUE)
```

We filtered the dataset on specific variables and conditions, to  make sure our hardware can process this large dataset. 

We only look at categories which included "Restaurants", which are not permanently closed. Secondly, based on the median of review_count we only included businesses with more then, or equal to 135 reviews. Additionally, we only selected the variables needed, which is still subject to some changes regarding the implementation of potential control variables. 

```{r}
# Looking for a good minimal threshold of amount of reviews a business has. 
summary(Data_Merged$review_count)

# Checking the amount of reviews per state to check which state is suitable. 
Data_Merged %>% count(state)

# Filtering the data of the merged data set
Data_Merged_Filtered <- Data_Merged %>% 
  filter(str_detect(categories, "Restaurants"),
         is_open == 1,
         review_count >= 135,
         state == "IL")%>% 
  select(review_count, name, state, categories, hours, business_id, text, stars.x, stars.y, user_id)
         
  # renaming the star.x, star.y and text variables
Data_Merged_Filtered <- Data_Merged_Filtered %>% 
  rename(Stars_Business = stars.x, Stars_Users = stars.y, Review = text) 

# Getting rid of the NA's
Data_Merged_Filtered <- na.omit(Data_Merged_Filtered)
```

As we conduct a sentiment analysis, we need to make sure reviews have a sufficient length to be suitable for analysis. Therefore we filtered the amount of words to be greater then 10). 

```{r}
 # Reviews >10 words. 
Data_Merged_Final<- Data_Merged_Filtered %>% filter((str_count(Review, " ") + 1) > 10)
```

