---
title: "Raw Data Exploration"
author: "Tarn"
date: "2025-03-12"
output: pdf_document: 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org/"))

library(ggplot2)
library(tidyverse)
library(here)
library(skimr)
```

## Loading in the data

After downloading the sampled_raw_data files and merging them, we can load in the complete raw dataset.

```{r, message=FALSE, warning=FALSE}
# Loading the Yelp data
Yelp <- read_csv(here("gen", "temp", "Yelp.csv"))
```

## Overview

Before starting into analysis, we start with a general exploration of the dataset. This allows us to understand its structure, identify potential issues such as missing values or inconsistent formatting, and to discover the types of variables included.

We begin by inspecting the structure of the data using `glimpse()` and summarizing each variable with `skim()`, which provides a compact summary including data types, number of missing values, and key distributional statistics.

```{r}
# Basic structure
glimpse(Yelp)

# Summary statistics and checking for missing values
skim(Yelp)
```

## Generating initial plots

```{r, echo = FALSE, warning = FALSE}
ggplot(Yelp, aes(x = state)) +
  geom_bar(fill = "lightblue", color = "black") +
  labs(title = "Number of Businesses by State", x = "State", y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

```{r, echo = FALSE}
ggplot(Yelp, aes(x = review_count)) +
  geom_histogram(binwidth = 50, fill = "darkorange", color = "black") +
  labs(title = "Distribution of Review Counts", x = "Review Count", y = "Frequency") +
  scale_x_continuous(limits = c(0, 1000)) 

```

```{r, echo = FALSE}
ggplot(Yelp, aes(x = as.factor(stars.x))) +
  geom_bar(fill = "lightgreen", color = "black") +
  labs(title = "Distribution of Business Star Ratings", x = "Stars", y = "Count")

```

```{r, echo = FALSE}
ggplot(Yelp, aes(x = as.factor(is_open))) +
  geom_bar(fill = "cyan", color = "black") +
  labs(title = "Count of Open vs. Closed Businesses", x = "Open (1=Yes, 0=No)", y = "Count")

```
